From Freebase to Wikidata: The Great Migration

### 2015-10-16 paper.tex
Tiny correction in Abstract. Correct categories.

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a~machine-readable form
are central for the data strategy of many projects and organizations.
The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
Due to the success of Wikidata, Google decided in 2014 to offer the content of Freebase
to the Wikidata community.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We describe the \emph{Primary Sources Tool}, which aims to facilitate
this and future data migrations.
Throughout the migration, we have gained insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

\category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces?Web-based interactions}
\category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
\category{K.4.3}{Computers and Society}{Organizational Impacts Computer-supported collaborative work}

>>>>

\begin{abstract}
Collaborative knowledge bases that make their data freely available in a~machine-readable form
are central for the data strategy of many projects and organizations.
The two major collaborative knowledge bases are Google's Freebase and Wikimedia's Wikidata.
Due to the success of Wikidata, Google decided in 2014 to offer the content of Freebase
to the Wikidata community.
In this paper, we describe the ongoing transfer efforts and data mapping challenges,
and provide an analysis of the effort so far.
We describe the \emph{Primary Sources Tool}, which aims to facilitate
this and future data migrations.
Throughout the migration, we have gained deep insights into both Wikidata and Freebase,
and share and discuss detailed statistics on both knowledge bases. 
\end{abstract}

% \category{CR number}{category}{sub-category}[optional subject descriptor]
\category{H.3.5}{Information Storage and Retrieval}{Online Information Systems}
\category{H.5.3}{Information Interfaces}{Group and Organization Interfaces}[Web-based interactions]
\category{I.2.4}{Artificial Intelligence}{Knowledge Representation}
\category{K.4.3}{Computers and Society}{Organizational Impacts}[Com\-puter-supported collaborative work]
